---
title: "Movie"
author: "Young Ho Lee"
date: "2017년 8월 22일"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Basic Packages
library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
library(gridExtra)
library(xgboost)

Sys.setenv(R_ZIPCMD= "C:/Rtools/bin/zip")
library(openxlsx)

options("scipen" = 100)

#setwd
knitr::opts_knit$set(root.dir = "D:/Data/contest/movie/movie_refined/")
```

# 1. Data Import
```{r}
list.files()
movie.flist.xlsx <- list.files()
fname.list <- substr(movie.flist.xlsx, 1, nchar(movie.flist.xlsx)-5)
# week.flist

for(i in 1:length(fname.list)){
  tmp.xlsx <- read.xlsx(paste0("movie_", i, ".xlsx"))
  names(tmp.xlsx)[5] <- "매출액점유율"
  tmp.xlsx <- tmp.xlsx %>%
    mutate(week = week.flist[i])
  assign(paste0("movie_", i), tmp.xlsx)
  message("[", paste0("movie_", i), "] has completed")
}
```

## 1) Merge Data
```{r}
movie_all <- NULL
for(i in 1:length(fname.list)){
  tmp <- get(paste0("movie_", i))
  movie_all <- rbind(movie_all, tmp)
}

movie_all <- movie_all %>%
  rename(rank = 순위,
         movie_name = 영화명,
         open_date = 개봉일,
         sales = 매출액, 
         sales_rate = 매출액점유율,
         total_sales = 누적매출액,
         attendance = 관객수,
         total_attendance = 누적관객수,
         screen = 스크린수,
         showing_frequency = 상영횟수,
         typical_nationality = 대표국적,
         nationality = 국적,
         production_company = 제작사,
         distributor = 배급사,
         grade = 등급,
         genre = 장르,
         director = 감독,
         actor_actress = 배우)
```

## 2) Split Data
```{r}
movie_sum <- movie_all %>%
  filter(rank == '합계') %>%
  select(rank, sales, total_sales, attendance, total_attendance, 
         screen, showing_frequency, week)

# setwd("D:/Data/contest/movie/")
# write.xlsx(movie_sum, "movie_sum.xlsx", row.names = FALSE)

movie_data <- movie_all %>%
  filter(rank != '합계')

movie_data$rank <- as.numeric(movie_data$rank)
movie_data$open_date <- as.numeric(movie_data$open_date)

# write.xlsx(movie_data, "movie_data.xlsx", row.names = FALSE)
```

## 3) Refined Data Import
```{r}
movie_data <- read.xlsx("D:/Data/contest/movie/movie_data_1.xlsx")
movie_sum <- read.xlsx("D:/Data/contest/movie/movie_sum.xlsx")

str(movie_data)
summary(movie_data)
```

# 2. Data Exploration
## 1) Column Explanaion
```{r}
names(movie_data)
unique(movie_data$typical_nationality)
# unique(movie_data$nationality)
unique(movie_data$grade)
unique(movie_data$genre)
# unique(movie_data$production_company)
```

## 2) Visualization
### 2-1) First Rank
```{r}
movie_data %>%
  filter(rank == 1) %>%
  group_by(movie_name) %>%
  summarise(count = n()) %>%
  filter(count >= 2) %>%
  ggplot(aes(x = movie_name, y = count, fill = movie_name)) +
  geom_col() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```

### 2-2) Grade
```{r}
movie_data %>%
  group_by(grade) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = grade, y = count, fill = grade)) +
  geom_col() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```

### 2-3) Sales
```{r}
movie_data %>%
  ggplot(aes(x = log(sales), y = log(total_attendance), color = sales)) +
  geom_point(shape = 21) + geom_line() -> g1

movie_data %>%
  ggplot(aes(x = sales_rate, y = log(total_attendance), color = sales_rate)) +
  geom_point(shape = 21) + geom_line() -> g2

grid.arrange(g1, g2, nrow = 2)
```

```{r}
movie_data %>%
  ggplot(aes(x = log(total_sales), y = log(total_attendance), color = total_sales)) +
  geom_point(shape = 21) + geom_line()
```

### 2-4) Screen / Showing Frequency
```{r}
movie_data %>%
  ggplot(aes(x = screen, y = log(total_attendance), color = screen)) +
  geom_point(shape = 21) + geom_line() -> g1

movie_data %>%
  ggplot(aes(x = showing_frequency, y = log(total_attendance), color = showing_frequency)) +
  geom_point(shape = 21) + geom_line() -> g2

grid.arrange(g1, g2, nrow = 2)
```

### 2-6) Typicial Nationality
```{r}
movie_data %>%
  group_by(typical_nationality) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = typical_nationality, y = count, fill = typical_nationality)) +
  geom_col() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 60, face = "italic", vjust = 1, hjust = 1))
```

```{r}
movie_data %>%
  group_by(typical_nationality) %>%
  summarise(count = n(), avg_total_attendance = mean(total_attendance)) %>%
  filter(count >= 200) %>%
  ggplot(aes(x = typical_nationality, y = avg_total_attendance, fill = typical_nationality)) +
  geom_col() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```

# 3. Data Handling
## 1) Grade
```{r}
grade.list <- unique(movie_data$grade)

# grade.list[c(1, 6, 7, 8, 14, 21, 24, 29, 41)]
# grade.list[c(2, 9, 16, 18, 20, 23, 25, 26, 35, 37, 39, 45)]
# grade.list[c(3, 15, 22, 27, 30, 42, 43, 46)]
# grade.list[c(4, 11, 12, 13, 17, 19, 28, 31, 32, 33, 34, 36, 38, 44, 47)]

movie_data[which(movie_data$grade ==  grade.list[1] | movie_data$grade == grade.list[6] | movie_data$grade ==  grade.list[7] | movie_data$grade ==  grade.list[8] | movie_data$grade ==  grade.list[14] | movie_data$grade ==  grade.list[21] | movie_data$grade ==  grade.list[24] | movie_data$grade ==  grade.list[29] | movie_data$grade ==  grade.list[41]), "grade"] <- "12세이상관람가"

movie_data[which(movie_data$grade ==  grade.list[2] | movie_data$grade == grade.list[9] | movie_data$grade ==  grade.list[16] | movie_data$grade ==  grade.list[18] | movie_data$grade ==  grade.list[20] | movie_data$grade ==  grade.list[23] | movie_data$grade ==  grade.list[25] | movie_data$grade ==  grade.list[26] | movie_data$grade ==  grade.list[35] | movie_data$grade ==  grade.list[37] | movie_data$grade ==  grade.list[39] | movie_data$grade ==  grade.list[45]), "grade"] <- "15세이상관람가"

movie_data[which(movie_data$grade ==  grade.list[3] | movie_data$grade == grade.list[15] | movie_data$grade ==  grade.list[22] | movie_data$grade ==  grade.list[27] | movie_data$grade ==  grade.list[30] | movie_data$grade ==  grade.list[42] | movie_data$grade ==  grade.list[43] | movie_data$grade ==  grade.list[46]), "grade"] <- "전체관람가"

movie_data[which(movie_data$grade ==  grade.list[4] | movie_data$grade == grade.list[11] | movie_data$grade ==  grade.list[12] | movie_data$grade ==  grade.list[13] | movie_data$grade ==  grade.list[17] | movie_data$grade ==  grade.list[19] | movie_data$grade ==  grade.list[28] | movie_data$grade ==  grade.list[31] | movie_data$grade ==  grade.list[32] | movie_data$grade ==  grade.list[33] | movie_data$grade ==  grade.list[34] | movie_data$grade ==  grade.list[36] | movie_data$grade ==  grade.list[38] | movie_data$grade ==  grade.list[44] | movie_data$grade ==  grade.list[47]), "grade"] <- "청소년관람불가"

movie_data[which(is.na(movie_data$grade) | movie_data$grade == grade.list[10] | movie_data$grade ==  grade.list[40]), "grade"] <- "미정"

movie_data$grade <- as.factor(movie_data$grade)
```

### 1-1) Grade_count
```{r}
movie_data %>%
  group_by(grade) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = grade, y = count, fill = grade)) +
  geom_col() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```

### 1-2) Grade_Total Attendance
```{r}
movie_data %>%
  group_by(grade) %>%
  summarise(avg_total_attendance = mean(total_attendance)) %>%
  ggplot(aes(x = grade, y = avg_total_attendance, fill = grade)) +
  geom_col()
```

```{r}
movie_data %>%
  ggplot(aes(x = grade, y = log(total_attendance), fill = grade)) +
  geom_jitter(color = 'grey', alpha = .2) +
  geom_violin(alpha = .7)
```


## 2) Genre
```{r}
split_genre <- function(x){
  strsplit(x, split = ',')[[1]][1]
}

movie_data$genre <- sapply(movie_data$genre, split_genre)

movie_data[which(is.na(movie_data$genre)), "genre"] <- "기타"

movie_data$genre <- as.factor(movie_data$genre)
```

### 2-1) Genre_Total Attendance
```{r}
movie_data %>%
  group_by(genre) %>%
  summarise(avg_total_attendance = mean(total_attendance)) %>%
  ggplot(aes(x = genre, y = avg_total_attendance, fill = genre)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```

```{r}
movie_data %>%
  ggplot(aes(x = genre, y = log(total_attendance), fill = genre)) +
  geom_jitter(color = 'grey', alpha = .2) +
  geom_violin(alpha = .7) + 
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```


## 3) Production Company
```{r}
movie_data %>%
  group_by(production_company) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

movie_data[which(is.na(movie_data$production_company)), "production_company"] <- "제작사 없음"
```

### 3-1) Production Company_Total Attendance
```{r}
movie_data %>%
  group_by(production_company) %>%
  summarise(count = n(), avg_total_attendance = mean(total_attendance)) %>%
  filter(count >= 50) %>%
  ggplot(aes(x = production_company, y = avg_total_attendance, fill = production_company)) +
  geom_col() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```


## 4) Distributor
```{r}
movie_data %>%
  group_by(distributor) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

movie_data[which(is.na(movie_data$distributor)), "distributor"] <- "배급사 없음"
```

### 4-1) Distritor_Total Attendance
```{r}
movie_data %>%
  group_by(distributor) %>%
  summarise(count = n(), avg_total_attendance = mean(total_attendance)) %>%
  filter(count >= 250) %>%
  ggplot(aes(x = distributor, y = avg_total_attendance, fill = distributor)) +
  geom_col() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```

## 5) Director
```{r}
movie_data %>%
  group_by(director) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

movie_data[which(is.na(movie_data$director)), "director"] <- "감독 없음"
```

### 5-1) Director_Total Attendance
```{r}
movie_data %>%
  group_by(director) %>%
  summarise(count = n(), avg_total_attendance = mean(total_attendance)) %>%
  filter(count >= 40) %>%
  ggplot(aes(x = director, y = avg_total_attendance, fill = director)) +
  geom_col() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```

## 6) Actor / Actress
```{r}
movie_data %>%
  group_by(actor_actress) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

movie_data[which(movie_data$genre == "애니메이션"), "actor_actress"] <- "애니메이션"
movie_data[which(is.na(movie_data$actor_actress)), "actor_actress"] <- "배우 없음"
```

## 7) Open Date
```{r}
split_year <- function(x){
  strsplit(x, split = '-')[[1]][1]
}

split_month <- function(x){
  strsplit(x, split = '-')[[1]][2]
}

split_day <- function(x){
  strsplit(x, split = '-')[[1]][3]
}

movie_data$open_year <- sapply(movie_data$open_date, split_year)
movie_data$open_month <- sapply(movie_data$open_date, split_month)
movie_data$open_day <- sapply(movie_data$open_date, split_day)

movie_data$open_year <- as.numeric(movie_data$open_year)
movie_data$open_month <- as.numeric(movie_data$open_month)
movie_data$open_day <- as.numeric(movie_data$open_day)
```

### 7-1) Year
```{r}
movie_data %>%
  group_by(open_year) %>%
  summarise(avg_total_attendance = mean(total_attendance)) %>%
  ggplot(aes(x = factor(open_year), y = avg_total_attendance, fill = factor(open_year))) +
  geom_col() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```

```{r}
movie_data %>%
  mutate(open_year = factor(open_year)) %>%
  ggplot(aes(x = open_year, y = log(total_attendance), fill = open_year)) +
  geom_boxplot() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```


### 7-2) Month
```{r}
movie_data %>%
  group_by(open_month) %>%
  summarise(avg_total_attendance = mean(total_attendance)) %>%
  ggplot(aes(x = factor(open_month), y = avg_total_attendance, fill = factor(open_month))) +
  geom_col()
```

```{r}
movie_data %>%
  mutate(open_month = factor(open_month)) %>%
  ggplot(aes(x = open_month, y = log(total_attendance), fill = open_month)) +
  geom_boxplot() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```


### 7-3) Day
```{r}
movie_data %>%
  group_by(open_day) %>%
  summarise(avg_total_attendance = mean(total_attendance)) %>%
  ggplot(aes(x = factor(open_day), y = avg_total_attendance, fill = factor(open_day))) +
  geom_col() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```

```{r}
movie_data %>%
  mutate(open_day = factor(open_day)) %>%
  ggplot(aes(x = open_day, y = log(total_attendance), fill = open_day)) +
  geom_boxplot() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1, hjust = 1))
```

## 8) Week
```{r}
movie_data$week_year <- sapply(movie_data$week, split_year)
movie_data$week_month <- sapply(movie_data$week, split_month)
movie_data$week_day <- sapply(movie_data$week, split_day)

movie_data$week_year <- as.numeric(movie_data$week_year)
movie_data$week_month <- as.numeric(movie_data$week_month)
movie_data$week_day <- as.numeric(movie_data$week_day)
```

## 9) Open Date_week Difference
```{r}
movie_data$diff <- as.Date(movie_data$week) - as.Date(movie_data$open_date)
movie_data$diff <- as.numeric(movie_data$diff)
```

```{r}
write.xlsx(movie_data, "movie_data.xlsx", row.names = FALSE)
```

# 4. Refined Data
## 1) Data Import
```{r}
movie_data_2 <- read.xlsx("D:/Data/contest/movie/movie_data_2.xlsx")

str(movie_data_2)
summary(movie_data_2)
```

## 2) Data Handling
### 2-1) Open Date
```{r}
# movie_data_2$open_date <- as.Date(movie_data_2$open_date)
## Imputation(total_attendance > 10,000 - googling + Excel / < 10,000 - mean)
movie_data_2[which(is.na(movie_data_2$open_date)), "open_date"] <- "2011-10-10"

split_year <- function(x){
  strsplit(x, split = '-')[[1]][1]
}

split_month <- function(x){
  strsplit(x, split = '-')[[1]][2]
}

split_day <- function(x){
  strsplit(x, split = '-')[[1]][3]
}

movie_data_2$open_year <- sapply(movie_data_2$open_date, split_year)
movie_data_2$open_month <- sapply(movie_data_2$open_date, split_month)
movie_data_2$open_day <- sapply(movie_data_2$open_date, split_day)

movie_data_2$open_year <- as.numeric(movie_data_2$open_year)
movie_data_2$open_month <- as.numeric(movie_data_2$open_month)
movie_data_2$open_day <- as.numeric(movie_data_2$open_day)
```

### 2-2) Rest
```{r}
# Week
# movie_data_2$week <- as.Date(movie_data_2$week)

# Actor_Actress
movie_data_2[which(is.na(movie_data_2$actor_actress2)), "actor_actress2"] <- movie_data_2[which(is.na(movie_data_2$actor_actress2)), "actor_actress1"]
movie_data_2[which(is.na(movie_data_2$actor_actress3)), "actor_actress3"] <- movie_data_2[which(is.na(movie_data_2$actor_actress3)), "actor_actress1"]

# Difference
movie_data_2$diff <- as.Date(movie_data_2$week) - as.Date(movie_data_2$open_date)
movie_data_2$diff <- as.numeric(movie_data_2$diff)

# Typicial Nationality
movie_data_2[which(is.na(movie_data_2$typical_nationality)), "typical_nationality"] <- "국가 없음"
```

### 2-3) Feature Selection
```{r}
movieData <- movie_data_2 %>%
  select(-c(rank, sales, sales_rate, total_sales, attendance, screen,
         showing_frequency, nationality, open_date, week))
```

### 2-4) Production Company
```{r}
movieData %>%
  group_by(production_company) %>%
  summarise(sum = sum(total_attendance)) %>%
  arrange(desc(sum)) -> productionCompany

productionCompany$main_productionCompany <- NA
productionCompany[2:26, ]$main_productionCompany <- productionCompany[2:26, ]$production_company
productionCompany[which(is.na(productionCompany$main_productionCompany)), "main_productionCompany"] <- "기타"

movieData <- merge(movieData, productionCompany[, c(1, 3)], by = c("production_company"), all.x = TRUE)
```

### 2-5) Distributor
```{r}
movieData %>%
  group_by(distributor) %>%
  summarise(sum = sum(total_attendance)) %>%
  arrange(desc(sum)) -> distributor

distributor$main_distributor <- NA
distributor[1:15, ]$main_distributor <- distributor[1:15, ]$distributor
distributor[which(is.na(distributor$main_distributor)), "main_distributor"] <- "기타"

movieData <- merge(movieData, distributor[, c(1, 3)], by = c("distributor"), all.x = TRUE)
```

### 2-6) Director
```{r}
# Director
movieData %>%
  group_by(director) %>%
  summarise(sum = sum(total_attendance)) %>%
  arrange(desc(sum)) -> director

director$main_director <- NA
director[1:50, ]$main_director <- director[1:50, ]$director
director[which(is.na(director$main_director)), "main_director"] <- "기타"

movieData <- merge(movieData, director[, c(1, 3)], by = c("director"), all.x = TRUE)
```

### 2-7) Typicial Nationality
```{r}
movieData %>%
  group_by(typical_nationality) %>%
  summarise(sum = sum(total_attendance)) %>%
  arrange(desc(sum)) -> typical_nationality

typical_nationality$main_nationality <- NA
typical_nationality[1:4, ]$main_nationality <- typical_nationality[1:4, ]$typical_nationality
typical_nationality[which(is.na(typical_nationality$main_nationality)), "main_nationality"] <- "기타"

movieData <- merge(movieData, typical_nationality[, c(1, 3)], by = c("typical_nationality"), all.x = TRUE)
```

### 2-8) Actor / Actress
```{r}
movieData %>%
  group_by(actor_actress1) %>%
  summarise(sum = sum(total_attendance)) %>%
  arrange(desc(sum)) -> actor1

actor1$main_actor_actress1 <- NA
actor1[c(1:51), ]$main_actor_actress1 <- actor1[c(1:51), ]$actor_actress1 # including animation
actor1[which(is.na(actor1$main_actor_actress1)), "main_actor_actress1"] <- "기타"

movieData <- merge(movieData, actor1[, c(1, 3)], by = c("actor_actress1"), all.x = TRUE)

movieData %>%
  group_by(actor_actress2) %>%
  summarise(sum = sum(total_attendance)) %>%
  arrange(desc(sum)) -> actor2

actor2$main_actor_actress2 <- NA
actor2[c(1:51), ]$main_actor_actress2 <- actor2[c(1:51), ]$actor_actress2 # including animation
actor2[which(is.na(actor2$main_actor_actress2)), "main_actor_actress2"] <- "기타"

movieData <- merge(movieData, actor2[, c(1, 3)], by = c("actor_actress2"), all.x = TRUE)

movieData %>%
  group_by(actor_actress3) %>%
  summarise(sum = sum(total_attendance)) %>%
  arrange(desc(sum)) -> actor3

actor3$main_actor_actress3 <- NA
actor3[c(1:51), ]$main_actor_actress3 <- actor3[c(1:51), ]$actor_actress3 # including animation
actor3[which(is.na(actor3$main_actor_actress3)), "main_actor_actress3"] <- "기타"

movieData <- merge(movieData, actor3[, c(1, 3)], by = c("actor_actress3"), all.x = TRUE)

movieData <- movieData %>%
  select(-c(production_company, distributor, director, typical_nationality, 
            movie_name, actor_actress1, actor_actress2, actor_actress3))
```

### 2-9) etc
```{r}
# Factoring
movieData$main_nationality <- as.factor(movieData$main_nationality)
movieData$grade <- as.factor(movieData$grade)
movieData$genre <- as.factor(movieData$genre)
movieData$main_productionCompany <- as.factor(movieData$main_productionCompany)
movieData$main_distributor <- as.factor(movieData$main_distributor)
movieData$main_director <- as.factor(movieData$main_director)

# etc
movieData$total_attendance <- ifelse(movieData$total_attendance <= 0, 1, movieData$total_attendance)
```

# 5. Modeling
```{r}
# Split train & test
set.seed(1234)
trainIndex <- sample(x = 1:nrow(movieData), size = 0.7 * nrow(movieData))
train <- movieData[trainIndex, ]
test <- movieData[-trainIndex, ]
```

```{r}
# XGBoost
trainLabel <- log(train$total_attendance)

trainMat <- model.matrix(log(total_attendance) ~ ., data = train)
testMat <- model.matrix(log(total_attendance) ~ ., data = test)
```

```{r}
params <- list(eta = 0.05, max.depth = 5,
               gamma = 0, colsample_bytree = 1,
               subsample = 1,
               objective = "reg:linear",
               eval_metric = "rmse")

set.seed(1234)
xgbcv <- xgb.cv(params = params,
                nrounds = 1000,
                nfold = 10,
                metrics = "rmse",
                data = trainMat,
                label = trainLabel,  
                verbose = 0)

xgb.best <- arrange(xgbcv$evaluation_log, test_rmse_mean)[1, ] 
xgb.best
```

```{r}
xgb <- xgboost(params = params,
                       data = trainMat,
                       label = trainLabel,
                       nrounds = 4000,
                       verbose = 1)

# xgb.best$iter
```

# 6. Model Evaluation
```{r}
rmsle <- function(pred, act) {
    if(length(pred) != length(act))
        stop("The length of two vectors are different")
    
    len <- length(pred)
    pred <- log(pred + 1)
    act <- log(act + 1)
    
    msle <- mean((pred - act)^2)
    
    return(sqrt(msle))
}
```

```{r}
xgb_pred <- predict(xgb, testMat)
xgb_pred <- exp(xgb_pred)
plot(xgb_pred)
```

```{r}
rmsle(xgb_pred, test$total_attendance)
rmsle1 <- rmsle(xgb_pred, test$total_attendance) # 1.797032
rmsle2 <- rmsle(xgb_pred, test$total_attendance) # 1.797032
rmsle3 <- rmsle(xgb_pred, test$total_attendance) # 1.704394
# 1500 : 1.653538
# 2000 : 1.626783
# 3000 : 1.59741
# 4000 : 1.580407
```

# 7. Real prediction
```{r}
realTest <- read.xlsx("D:/Data/contest/movie/test.xlsx")

realTest$total_attendance <- NA
realTest$total_attendance <- 5000

realTest <- realTest %>%
  select(-movie_name)

for(i in 4:9){
  realTest[, i] <- as.factor(realTest[, i])
}
for(i in 4:12){
    names(realTest)[i] <- paste0("main_", names(realTest)[i])
}
names(realTest)[7] <- "grade"
names(realTest)[8] <- "genre"
names(realTest)[4] <- "main_nationality"
names(realTest)[11] <- "main_productionCompany"

realTest <- realTest %>%
  select(total_attendance, grade, genre, open_year, open_month, open_day, week_year,
         week_month, week_day, diff, main_productionCompany, main_distributor,
         main_director, main_nationality, main_actor_actress1, main_actor_actress2,
         main_actor_actress3)

test_real <- rbind(realTest, test)
realMat <- model.matrix(log(total_attendance) ~ ., data = test_real)

real_pred <- predict(xgb, realMat)
real_pred <- exp(real_pred)

real_pred[1:3] # 3080256 1158378 5578043
```

